---
title: Data Augmentation"
format: html
editor: visual
---

### Read Data

```{r read_data}
library(readr)

nih_awd_df <- readr::read_csv("NIH_Award\\RePORTER_PRJ_C_FY2024.csv")
nsf_awd_df <- readr::read_csv("nsf_award.csv")

head(nih_awd_df)
head(nsf_awd_df)
```

Feature engineer nih_awd_df. Variables of interest: PI_IDS, PI_NAME, ORG_NAME

Check if the same award can be assigned to multiple organizations.

```{r nih_data_exploration1}
library(dplyr)

# Check if the same award can be assigned to multiple organizations
nih_awd_df %>%
  select(PI_IDS, PI_NAMEs, ORG_NAME) %>% 
  mutate(ORG_NAME = strsplit(ORG_NAME, ";"),
         org_name_count = sapply(ORG_NAME, length)) %>% 
  filter(org_name_count > 1)
```

```{r nih_feature_engineering}
library(dplyr)
library(tidyr)

nih_awd_df <- nih_awd_df %>%
  select(PI_IDS, PI_NAMEs, ORG_NAME) %>% 
  mutate(PI_IDS = strsplit(PI_IDS, ";"),
         PI_NAMEs = strsplit(PI_NAMEs, ";")) %>% 
  unnest(c(PI_IDS, PI_NAMEs, ORG_NAME))

head(nih_awd_df)
```

Luckily for nsf_awd_df, data is already unnested.


### Data Transformation

Remove "(contact)", "(nickname)", "-", and extra whitespace at the end of PI_IDS and PI_NAMEs
```{r}
# Remove parentheses, quotes, hyphens, and extra whitespace
nih_awd_df$PI_NAMEs <- gsub("\\(.*?\\)|[\"']|-", "", nih_awd_df$PI_NAMEs)  # Remove (), quotes, and -
nih_awd_df$PI_NAMEs <- gsub("\\s+", " ", nih_awd_df$PI_NAMEs)  # Replace multiple spaces with a single space
nih_awd_df$PI_NAMEs <- trimws(nih_awd_df$PI_NAMEs)  # Trim leading/trailing whitespace

nih_awd_df$PI_IDS <- gsub("\\(.*?\\)|[\"']|-", "", nih_awd_df$PI_IDS)  # Remove (), quotes, and -
nih_awd_df$PI_IDS <- gsub("\\s+", " ", nih_awd_df$PI_IDS)  # Replace multiple spaces with a single space
nih_awd_df$PI_IDS <- trimws(nih_awd_df$PI_IDS)  # Trim leading/trailing whitespace

# View the transformed dataset
head(nih_awd_df)
```


```{r}
# Function to clean and split names
clean_names <- function(name) {
  # Split into parts based on comma and space
  parts <- strsplit(name, ",\\s*")[[1]]
  
  # If there's no comma, assume the entire name is the last name
  if (length(parts) < 2) {
    last <- parts[1]
    first <- ""
    middle <- ""
  } else {
    last <- parts[1]
    first_middle <- strsplit(parts[2], "\\s+")[[1]]
    first <- first_middle[1]
    middle <- if (length(first_middle) > 1) {
      paste(first_middle[2:length(first_middle)], collapse = " ")
    } else {
      ""
    }
  }
  
  # Return as a data frame row
  data.frame(First = first, Middle = middle, Last = last, stringsAsFactors = FALSE)
}

# Apply the function to each name
name_data <- lapply(nih_awd_df$PI_NAMEs, clean_names) %>%
  bind_rows()

# Combine with the original data
nih_awd_df <- cbind(name_data, nih_awd_df)

head(nih_awd_df)

# TODO Resolve duplicates by selecting the first and last name pair, duplicates should be possible though

# Add a new column for full name using base R
nih_awd_df$FullName <- trimws(paste(nih_awd_df$First, nih_awd_df$Last))

head(nih_awd_df)
```

### Data Augmentation

Join nih_awd_df and generated_author_info by name

```{r read_data2}
library(readr)

generated_author_info_clean <- read_csv("generated_author_info_clean.csv")
csrankings_clean <- read_csv("csrankings_clean.csv")

tail(generated_author_info_clean)
tail(csrankings_clean)
```

Fix nih_awd_df such that name is in title format

```{r}
library(dplyr)
library(stringr)

nih_awd_df_clean <- nih_awd_df %>% 
  mutate(name = stringr::str_to_title(FullName)) %>% 
  rename(pi_id = PI_IDS,
         organization = ORG_NAME) %>% 
  select(pi_id, name, organization)
```

Name is now consistent among both datasets

TODO: group by name and get count of observations as num of NIH Awards

```{r}
num_awards <- nih_awd_df_clean %>% 
  group_by(name, pi_id) %>% 
  summarize(num_of_nih_awds = n())

head(num_awards)
```

Left join num_awds with generated_author_info (such that it joins with number of awards and NA if there is no award)

```{r}
library(dplyr)

generated_author_info_clean %>% 
  left_join(num_awards) %>% 
  filter(!is.na(num_of_nih_awds))
```

Aggregate generated_author_info to sum the number of publications and adjusted count, so each person has 1 observation

```{r}
library(dplyr)

generated_author_info_aggregated <- generated_author_info_clean %>% 
  group_by(name) %>% 
  summarize(
    dept = first(dept),
    total_publications = sum(count),
    adjusted_total_publications = sum(adjusted_count)
  )
```

Left join this new aggregated dataset with num_awards

```{r}
library(dplyr)

author_nih_award_info <- generated_author_info_aggregated %>% 
  left_join(num_awards, by="name") %>% 
  mutate(num_nih_awds = if_else(is.na(num_of_nih_awds), 0, num_of_nih_awds)) %>% 
  select(-num_of_nih_awds)

head(author_nih_award_info)
```

TODO: Join with csrankings


### Preliminary models

```{r}
mod1 <- lm(num_nih_awds ~ adjusted_total_publications, data=author_nih_award_info)

summary(mod1)
```

The number of nih_awards is positively associated with adjusted total publications



