---
title: Data Augmentation"
format: html
editor: visual
---

### Read Data

```{r read_data}
library(readr)

# Import augmented datasets
nih_awd_df <- readr::read_csv("NIH_Award\\RePORTER_PRJ_C_FY2024.csv")
nsf_awd_df <- readr::read_csv("nsf_awd_df2.csv")

head(nih_awd_df)
head(nsf_awd_df)
```

## Data Exploration

### NIH Award

Check if the same award can be assigned to multiple organizations.

```{r nih_data_exploration1}
library(dplyr)

nih_awd_df %>%
  select(PI_IDS, PI_NAMEs, ORG_NAME) %>% 
  mutate(ORG_NAME = strsplit(ORG_NAME, ";"),
         org_name_count = sapply(ORG_NAME, length)) %>% 
  filter(org_name_count > 1)
```

### NSF Award


## Data Cleaning

### NIH Award

Select key features, and unnest PI_NAME, PI_IDs (Awards can have multiple PIs)

```{r nih_feature_engineering}
library(dplyr)
library(tidyr)

nih_awd_df <- nih_awd_df %>%
  select(PI_IDS, PI_NAMEs, ORG_NAME) %>% 
  mutate(PI_IDS = strsplit(PI_IDS, ";"),
         PI_NAMEs = strsplit(PI_NAMEs, ";")) %>% 
  unnest(c(PI_IDS, PI_NAMEs, ORG_NAME))

head(nih_awd_df)
```

Clean name format to be consistent with Assignment 1.

Remove "(contact)", "(nickname)", "-", and extra whitespace at the end of PI_IDS and PI_NAMEs.

```{r}
# Remove parentheses, quotes, hyphens, and extra whitespace
nih_awd_df$PI_NAMEs <- gsub("\\(.*?\\)|[\"']|-", "", nih_awd_df$PI_NAMEs)  # Remove (), quotes, and -
nih_awd_df$PI_NAMEs <- gsub("\\s+", " ", nih_awd_df$PI_NAMEs)  # Replace multiple spaces with a single space
nih_awd_df$PI_NAMEs <- trimws(nih_awd_df$PI_NAMEs)  # Trim leading/trailing whitespace

nih_awd_df$PI_IDS <- gsub("\\(.*?\\)|[\"']|-", "", nih_awd_df$PI_IDS)  # Remove (), quotes, and -
nih_awd_df$PI_IDS <- gsub("\\s+", " ", nih_awd_df$PI_IDS)  # Replace multiple spaces with a single space
nih_awd_df$PI_IDS <- trimws(nih_awd_df$PI_IDS)  # Trim leading/trailing whitespace

# View the transformed dataset
head(nih_awd_df)
```

```{r}
# Function to clean and split names
clean_names <- function(name) {
  # Split into parts based on comma and space
  parts <- strsplit(name, ",\\s*")[[1]]
  
  # If there's no comma, assume the entire name is the last name
  if (length(parts) < 2) {
    last <- parts[1]
    first <- ""
    middle <- ""
  } else {
    last <- parts[1]
    first_middle <- strsplit(parts[2], "\\s+")[[1]]
    first <- first_middle[1]
    middle <- if (length(first_middle) > 1) {
      paste(first_middle[2:length(first_middle)], collapse = " ")
    } else {
      ""
    }
  }
  
  # Return as a data frame row
  data.frame(First = first, Middle = middle, Last = last, stringsAsFactors = FALSE)
}

# Apply the function to each name
name_data <- lapply(nih_awd_df$PI_NAMEs, clean_names) %>%
  bind_rows()

# Combine with the original data
nih_awd_df <- cbind(name_data, nih_awd_df)

head(nih_awd_df)

# TODO Resolve duplicates by selecting the first and last name pair, duplicates should be possible though

# Add a new column for full name using base R
nih_awd_df$FullName <- trimws(paste(nih_awd_df$First, nih_awd_df$Last))

head(nih_awd_df)
```

Fix nih_awd_df such that name is in title format

```{r}
library(dplyr)
library(stringr)

nih_awd_df_clean <- nih_awd_df %>% 
  mutate(name = stringr::str_to_title(FullName)) %>% 
  rename(pi_id = PI_IDS,
         organization = ORG_NAME) %>% 
  select(pi_id, name, organization)
```

### NSF Award

Luckily for NSF, data is already unnested.

Make name format consistent with A1, an NIH Award.

```{r}
library(dplyr)

clean_names2 <- function(name) {
  parts <- strsplit(name, " ")[[1]]
  first = parts[1]
  last = parts[length(parts)]
  
  # Return as a data frame row
  data.frame(First = first, Last = last, stringsAsFactors = FALSE)
}

# Apply the function to each name
name_data <- lapply(nsf_awd_df$pi_full_name, clean_names2) %>%
  bind_rows()

# Combine with the original data
nsf_awd_df <- cbind(name_data, nsf_awd_df)

head(nsf_awd_df)

# TODO Resolve duplicates by selecting the first and last name pair, duplicates should be possible though

# Add a new column for full name using base R
nsf_awd_df$FullName <- trimws(paste(nsf_awd_df$First, nsf_awd_df$Last))

head(nsf_awd_df)
```

Streamline columns

```{r}
library(dplyr)
library(stringr)

nsf_awd_df_clean <- nsf_awd_df %>% 
  rename(name = FullName) %>% 
  mutate(name = str_to_title(name))

head(nsf_awd_df_clean)
```

Aggregate by name

```{r}
nsf_award_names <- nsf_awd_df_clean %>% 
  group_by(name) %>% 
  summarise(
    num_nsf_awds = n()
  )

head(nsf_award_names)
```


### Data Visualization

```{r data_visualization}
# View datasets

head(nih_awd_df)
head(nsf_awd_df)
```
Visual 1: Bar chart of the top 6 organizations with the most NIH projects

```{r}
library(dplyr)
library(ggplot2)

nih_awd_org <- nih_awd_df %>% 
  group_by(ORG_NAME) %>% 
  summarise(
    num_awards = n()
  ) %>% 
  arrange(desc(num_awards)) %>% 
  slice(1:6)

# Create the bar plot
ggplot(nih_awd_org, aes(x = ORG_NAME, y = num_awards, fill = ORG_NAME)) +
  geom_bar(stat = "identity") +  # Use stat = "identity" for bar heights based on y values
  labs(
    title = "Number of NIH Awards by Organization",
    x = "Organization Name",
    y = "Number of Awards"
  ) +
  theme_minimal() +  # Use a minimal theme for a clean look
  theme(
    axis.text.x = element_blank(),
    plot.title = element_text(hjust = 0.5, size = 12, face = "bold")  # Center and style the title
  ) +
  scale_fill_viridis_d()  # Use a color scale for the bars (optional)
```

Visual 2: Bar chart of top 6 organizations with the most NSF projects

```{r}
library(dplyr)
library(ggplot2)

nsf_awd_org <- nsf_awd_df %>% 
  group_by(org_name) %>% 
  summarise(
    num_awards = n()
  ) %>% 
  arrange(desc(num_awards)) %>% 
  slice(1:6)

# Create the bar plot
ggplot(nsf_awd_org, aes(x = org_name, y = num_awards, fill = org_name)) +
  geom_bar(stat = "identity") +  # Use stat = "identity" for bar heights based on y values
  labs(
    title = "Number of NSF Awards by Organization",
    x = "Organization Name",
    y = "Number of Awards"
  ) +
  theme_minimal() +  # Use a minimal theme for a clean look
  theme(
    axis.text.x = element_blank(),
    plot.title = element_text(hjust = 0.5, size = 12, face = "bold")  # Center and style the title
  ) +
  scale_fill_viridis_d()  # Use a color scale for the bars (optional)
```


## Data Augmentation


```{r read_data2}
library(readr)

generated_author_info_clean <- read_csv("generated_author_info_clean.csv")
csrankings_clean <- read_csv("csrankings_clean.csv")
field_conference <- read_csv("datasets\\field_conference.csv")
conference_ranking <- read_csv("datasets\\conference_ranking.csv")

tail(generated_author_info_clean)
tail(csrankings_clean)
head(field_conference)
head(conference_ranking)
```
Join field conference and conference_ranking.

```{r}
library(dplyr)
library(stringr)

new_generated_author_info <- generated_author_info_clean %>% 
  mutate(conference = str_to_upper(area)) %>% 
  inner_join(conference_ranking %>% rename(conference = Antonym)) %>% 
  inner_join(field_conference) %>% 
  select(-area)

head(new_generated_author_info)
```

Okay, now do aggregations.

### Analysis

Explore trends and patterns in publication counts based on NIH/NSF funding

```{r join_nsf_nih}
aggregated_nih_df <- nih_awd_df_clean %>% 
  group_by(name) %>% 
  summarise(
    total_nih_awards = n()
  )

aggregated_nsf_df <- nsf_awd_df_clean %>% 
  group_by(name) %>% 
  summarise(
    total_nsf_awards = n()
  )

author_award_info <- new_generated_author_info %>% 
  left_join(aggregated_nih_df, by='name') %>% 
  left_join(aggregated_nsf_df, by='name') %>% 
  mutate(total_nih_awards = if_else(is.na(total_nih_awards), 0, total_nih_awards),
         total_nsf_awards = if_else(is.na(total_nsf_awards), 0, total_nsf_awards),
         total_awards = total_nih_awards + total_nsf_awards)
head(author_award_info)
```

```{r}
temp <- author_award_info %>% 
  group_by(conference) %>% 
  summarise(
    total_publications = sum(count),
    total_adjusted_publications = sum(adjusted_count),
    Rank = first(Rank),
    field = first(field),
    nih_awards = sum(total_nih_awards),
    nsf_awards = sum(total_nsf_awards),
    total_awards = sum(total_awards)
  )

mod10 <- lm(total_publications ~ nsf_awards*field + nih_awards*field, data=temp)
summary(mod10)
```







Name is now consistent among both datasets.

```{r}
num_awards <- nih_awd_df_clean %>% 
  group_by(name, pi_id) %>% 
  summarize(num_of_nih_awds = n())

head(num_awards)
```

Left join num_awds with generated_author_info (such that it joins with number of awards and NA if there is no award)

```{r}
library(dplyr)

generated_author_info_clean %>% 
  left_join(num_awards) %>% 
  filter(!is.na(num_of_nih_awds))
```

Aggregate generated_author_info to sum the number of publications and adjusted count, so each person has 1 observation

```{r}
library(dplyr)

author_nih_award_info <- generated_author_info_clean %>% 
  left_join(num_awards, by="name") %>% 
  mutate(num_nih_awds = if_else(is.na(num_of_nih_awds), 0, num_of_nih_awds)) %>% 
  select(-num_of_nih_awds)

head(author_nih_award_info)
```

```{r}
library(dplyr)

author_award_info <- author_nih_award_info %>% 
  left_join(nsf_award_names, by="name") %>% 
  mutate(num_nsf_awds = if_else(is.na(num_nsf_awds), 0, num_nsf_awds),
         total_grant_awards = num_nih_awds + num_nsf_awds) %>% 
  arrange(desc(total_grant_awards))

head(author_award_info)
```

Join with conference ranking and field_conference

### Preliminary models

```{r}
mod1 <- lm(total_grant_awards ~ adjusted_total_publications, data = author_award_info)

summary(mod1)
```

```{r}
library(dplyr)
mod2 <- lm(num_nih_awds ~ adjusted_total_publications, data = author_award_info)

summary(mod2)

mod3 <- lm(num_nsf_awds ~ adjusted_total_publications, data = author_award_info)

summary(mod3)
```

There is not enough statistical evidence that the adjusted number of total publications is associated with num_nih_awds.


The number of nih_awards is positively associated with adjusted total publications

What if we aggregate by department?

```{r}
department_award_info <- author_award_info %>% 
  group_by(dept) %>% 
  summarize(
    nsf_awards = sum(num_nsf_awds),
    nih_awards = sum(num_nih_awds),
    total_publications = sum(total_publications),
    adjusted_total_publications = sum(adjusted_total_publications),
    total_awards = nsf_awards + nih_awards
  )

head(department_award_info)
```


```{r}
mod4 <- lm(adjusted_total_publications ~ nih_awards, data = department_award_info)
summary(mod4)

mod5 <- lm(adjusted_total_publications ~ nsf_awards, data = department_award_info)
summary(mod5)

mod6 <- lm(adjusted_total_publications ~ nih_awards + nsf_awards, data = department_award_info)
summary(mod6)
```




